---
title: "Mini-Project 2"
author: "Lidia Ortiz"
date: "March 24, 2017"
output: html_document
---


## Loading the data


```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
library(dplyr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(tidyverse)
```


```{r}
Joined_table<- candidates%>%
  inner_join(contributions, by=c("cand_id", "cand_id"))%>%
   filter(cand_office == "H", cand_election_yr == 2012, cand_office_state == c("ME", "MA", "IL"))
```

```{r}
Joined_table%>%
  group_by(cand_name, cand_office_state, cand_party_affiliation)%>%
  summarize(Total_contr = sum(transaction_amt), N =n(), avg = Total_contr/N)%>%
  arrange(desc(Total_contr))
```

Suggestions: 
facet-wrap by state
color = party : red/blue/green
bar graph

  Title: Contribution to the 2012 House Election in selected states 
  
  Context of post: Rather than examining committee contribution at a presidential level, we decided to examine contributions at a local level. Since examining all the house candidates would create a graphic that is rather clustered, we decided to examine the amount in three states that are of particular interest to us. These states are Illinois, Maine, Massachussetts.
  
  General Conclution:

